Contextual Combinatorial Cascading Bandits

### 2016-01-18 contextual combinatorial cascading bandits.tex

% my settings
\usepackage{amssymb,amsfonts,amsmath,bbm}
\usepackage{mathrsfs}
\usepackage[all]{xy}
\usepackage{empheq}
\usepackage{algorithm,algorithmic}
\usepackage{multirow}
\usepackage{ifthen}
\usepackage[usenames]{color}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{epstopdf}
%\usepackage{epsfig}
%\usepackage{times}
%\usepackage{helvet}
%\usepackage{courier}
%\usepackage{graphicx,subfigure}
%\usepackage{pdfpages}
%\usepackage{multirow}
%\usepackage{multicol}

\newcommand{\bbeta}{\boldsymbol{\beta}}
\newcommand{\EE}{\mathbb{E}}
\newcommand{\II}{\mathbb{I}}
\newcommand{\PP}{\mathbb{P}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\bT}{\mathbb{T}}
\newcommand{\bOne}{\mathbbm{1}}
\newcommand{\bA}{\mathbf{A}}
\newcommand{\ba}{\mathbf{a}}
\newcommand{\bB}{\mathbf{B}}
\newcommand{\bO}{\mathbf{O}}
\newcommand{\br}{\mathbf{r}}
\newcommand{\bU}{\mathbf{U}}
\newcommand{\bV}{\mathbf{V}}
\newcommand{\bw}{\mathbf{w}}
\newcommand{\bX}{\mathbf{X}}
\newcommand{\bY}{\mathbf{Y}}
\newcommand{\cA}{\mathcal{A}}
\newcommand{\cB}{\mathcal{B}}
\newcommand{\cH}{\mathcal{H}}
\newcommand{\cS}{\mathcal{S}}
\newcommand{\argmax}{\mathrm{argmax}}
\newcommand{\trace}{\mathrm{trace}}
\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\norm}[1]{\| #1 \|}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{remark}[theorem]{Remark}
\newtheorem{proposition}[theorem]{Proposition}%[chapter]
\newtheorem{definition}[theorem]{Definition}%[chapter]
\newtheorem{corollary}[theorem]{Corollary}%[chapter]
\newtheorem{lemma}[theorem]{Lemma}%[chapter]
\newtheorem{example}[theorem]{Example}
\newenvironment{proof}{\noindent {\textbf{Proof. }}}{$\Box$ \medskip}

@@

\section{Problem Formulation}

At time $t$, feature vectors $x_{t,a} \in \RR^{d \times 1}$ with $\norm{x_{t,a}}_2 \leq 1$ for every base arm $a \in E$ are revealed to the learning agent; the feature vectors combine both the information of the user and the corresponding base arm. \shengyu{Add a standard/typical example (just one sentence) to illustrate the combination?} Then the learning agent recommends a feasible action $\bA_t=(\ba_{1}^t,...,\ba_{\abs{\bA_t}}^t) \in \cS$ to a user, where notice that the length of the action is not fixed. Starting from the first item $\ba_{1}^t$, the user checks the items $(\ba_{1}^t,...,\ba_{\abs{\bA_t}}^t)$ one by one in that order. The checking process stops if the user clicks \shengyu{selects?} on one item or has checked all items without clicking \shengyu{selecting?} anyone. We use Bernoulli random variable $\bw_{t}(a) \in \{0,1\}$ as the {\em weight} of base arm $a$ at time $t$ to indicate whether the user has clicked on $a$ or not.

Let $\cH_t$ denote the history before the learning agent chooses action at time $t$.
Thus $\cH_t$ contains all information and observations at time $s < t$ and context information at time $t$. Given history $\cH_t$, we assume $\bw_{t,a}$'s are mutually independent and satisfy
\begin{equation} % eq:expectation
  \label{eq:expectation}
  \EE[\bw_{t,a} | \cH_t] = \theta_{\ast}^{\top} x_{t,a},
\end{equation}
where $\theta_{\ast}$ is an unknown $d$-dimensional vector with the assumption that $\norm{\theta_{\ast}}_2 \leq 1$ and $0 \leq \theta_{\ast}^{\top} x_{t,a} \leq 1$ for all $t, a$. 
We define random variable $\bO_t$ as the number of observed base arms in $\bA_t$, that is, for some $k=1,2,\ldots, \abs{\bA_t}$, 
$$
  \bO_t = k, \text{ if } \bw_t(\ba_j^t)=0, \forall\, j < k \text{ and } \bw_t(\ba_k^t) = 1,
$$
or 
$$
  \bO_t = \abs{\bA_t}, \text{ if }\bw_t(\ba_j^t) = 0, ~~ \forall\, j \leq \abs{\bA_t}.
$$
At the end of every time $t$, the agent observes the first $\bO_t$ items of $\bA_t$. We say that item $a$ is {\it observed} if $a = \ba_k^t$ for some $k \leq \bO_t$. 
Thus, $\cH_t$ consists of $\{x_s, \bA_s = (\ba_{1}^s,...,\ba_{\abs{\bA_s}}^s), \bO_s, \bw_s(\ba_k^s),x_t \mid  k \in[\bO_s], 1 \le s<t \}$.

The agent receives some reward if the user clicks on some item. Suppose we consider the position discount: if the user clicks on the $k$-th item, then the learning agent receives reward $0 \leq \gamma_k \leq 1$. Usually the importance of the positions is decreasing: the first position is most important. So it is a reasonable assumption that
$$
  1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0.
$$
At the end of time $t$, the learning agent observes $\bO_t, \bw_t(\ba_k^t), k \leq \bO_t$ and receives reward
$$
  \br_t = \bw_t(\ba_{\bO_t}^t) \gamma_{\bO_t} = \bigvee_{k=1}^{\abs{\bA_t}} \gamma_k \bw_t(\ba_k^t).
$$
where we use the notation that $\bigvee_{k=1}^n a_k = \max_{1 \leq k \leq n} a_k$. Notice that the order of $\bA_t$ affects both the feed back and the reward.

Now let us introduce a function $f$ on $A = (a_1,...,a_{\abs{A}}) \in \cS, w = (w(1),...,w(L))$ by
\begin{align}
  &f : \cS \times [0,1]^E \to [0,1] \nonumber \\
  &f(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_{k} \prod_{i=1}^{k-1} (1 - w(a_i)) w(a_k).
  \label{eq:functionf}
\end{align}
Then we have $\br_t = f(\bA_t, \bw_t)$ and $\EE[\br_t] = f(\bA_t, \theta_{\ast}^{\top}x_t)$ where $x_t = (x_{t,1}, \cdots, x_{t,L}) \in \RR^{d \times L}$. Let 
\begin{align*}
  A_t^{\ast} &= \argmax_{A\in \cS} f(A,\theta_{\ast}^{\top}x_t),\\
  f_t^{\ast} &= f(A_t^{\ast}, \theta_{\ast}^{\top}x_t).
\end{align*}
The goal of our learning algorithm is to minimize the expected cumulative regret in $T$ steps
$$
  R(T) = \EE\left[\sum_{t=1}^T R(t, \bA_t)\right].
$$
where $R(t, A) = f_t^{\ast} - f(A, \theta_{\ast}^{\top}x_t)$.

The above formulation is on the disjunctive objective, that is, at a time step the agent stops as soon as she reveals a base arm at a position $k$ in the sequence with weight $1$ and she receives reward $\gamma_k$ as the result. 
Similarly, we could also consider the case of conjunctive objective. 
We also use Bernoulli random variable $\bw_{t}(a) \in \{0,1\}$ to indicate the weight of item $a$ at time $t$ satisfying Equation \eqref{eq:expectation}). 
The learning agent observes all items until the first one with weight $0$. 
Suppose we also consider partial reward: if the $k$-th item is the first item with weight $0$, then the learning agent receives reward $\gamma_k'$; if all items have weight $1$, the learning agent receives reward $1$. 
The more items the learning agent reveals, the more reward the agent should receive. It is reasonable to assume that
$$
  0 = \gamma'_1 \leq \gamma'_2 \leq \cdots \leq \gamma'_K \leq 1.
$$
At the end of time $t$, the learning agent observes $\bO_{\wedge, t}, \bw_t(\ba_k^t), k \leq \bO_{\wedge, t}$ and receives reward $\br_{\wedge, t}$:
\begin{align*}
  \br_{\wedge, t} &= \begin{cases}
    \gamma_{\bO_{\wedge, t}}'  &\text{if } \bw_t(\ba_{\bO_{\wedge, t}}^t) = 0,\\
    1 &\text{if } \bw_t(\ba_{\bO_{\wedge, t}}^t) = 1,
  \end{cases}\\
  &=\begin{cases}
    \gamma_{k}'  &\text{if } \bw_t(\ba_{i}^t) = 1, i < k, \bw_t(\ba_{k}^t) = 0,\\
    1 &\text{if } \bw_t(\ba_{i}^t) = 1, i\leq \abs{\bA_t}.
  \end{cases}
\end{align*}

If we define a function $f_{\wedge}$ on $A = (a_1, \ldots, a_{\abs{A}}) \in \cS, w = (w(1), \ldots, w(L))$ by
\begin{align}
  &f_{\wedge} : \cS \times [0,1]^E \to [0,1] \nonumber \\
  &f_{\wedge}(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_k' \prod_{i = 1}^{k - 1} w(a_i)(1 - w(a_k)) + \prod_{i=1}^{\abs{A}}w(a_i),
  \label{eq:functionfstar}
\end{align}
then we have $\br_{\wedge, t} = f_{\wedge}(\bA_t, \bw_t)$ and $\EE[\br_{\wedge, t}] = f_{\wedge}(\bA_t, \theta_{\ast}^{\top}x_t)$ where $x_t = (x_{t,1}, \cdots, x_{t,L}) \in \RR^{d \times L}$. To simplify notations, we assume 
$$
  \gamma_k' = 1 - \gamma_k.
$$
Then it holds that
\begin{equation} %eq:ConDisRelation
  \label{eq:ConDisRelation}
  f_{\wedge}(A, w) = 1 - f(A, 1 - w).
\end{equation}
Let 
\begin{align*}
  A_{\wedge, t}^{\ast} &= \argmax_{A\in \cS} f(A,\theta_{\ast}^{\top}x_t),\\
  f_{\wedge, t}^{\ast} &= f(A_t^{\ast}, \theta_{\ast}^{\top}x_t).
\end{align*}
For the conjunctive objective, the goal of our learning algorithm is to minimize the expected cumulative regret in $T$ steps
$$
  R_{\wedge}(T) = \EE\left[\sum_{t=1}^T R_{\wedge}(t, \bA_t)\right].
$$
where $R_{\wedge}(t, A) = f_{\wedge, t}^{\ast} - f_{\wedge}(A, \theta_{\ast}^{\top}x_t)$.

We formulate the problem of {\em contextual combinatorial cascading bandit} as follows. Suppose we have a finite set  $E=\{1,...,L\}$ of $L$ \textit{ground items}, also referred to as {\em base arms}. Let $\cS$ be the set of \textit{feasible actions}. For any feasible action $A \in \cS$, $A$ has an underlying set, which is a subset of $E$, together with a structure $s_A$. In website recommender systems, a feasible action $A$ is a set of $K$ websites listed in linear order and the user, faced with such a website list, will check the website one by one from the beginning. In social influence problem, a feasible action is a subset of people in graph structure. In the rest of the paper, we abuse the notation of $A$ to denote the feasible action and also the corresponding underlying set. We define the {\it size} of feasible action $A$ to be the number of base arms in the underlying set of $A$, denoted by $|A|$. We assume all feasible actions considered in this paper have size at most $K$. In many of applications, the expected reward of an action relates not only the underlying set but also the structure, or the order of the base arms. For example in recommender systems, to improve user experience, the items with higher preference will be listed higher.

At time $t$, feature vectors $x_{t,a} \in \RR^{d \times 1}$ with $\norm{x_{t,a}}_2 \leq 1$ for every base arm $a \in E$ are revealed to the learning agent; the feature vectors combine both the information of the user and the corresponding base arm. \shengyu{Add a standard/typical example (just one sentence) to illustrate the combination?} For example, suppose the user at time $t$ is represented by the feature vector $u_t$ and the feature vector of the base arm $a$ is $v_a$, then we can let $x_{t,a}$ be $(u_t, v_a)$ which combines both the information of the user and the base arm. \shuai{I have added one sentence.} Then the learning agent recommends a feasible action $\bA_t=\{ \ba_{1}^t,...,\ba_{\abs{\bA_t}}^t \} \in \cS$ to the user. Notice that the size of the action is not fixed. Then according to the user behavior and the structure of the action $\bA_t$, we observe the weights of base arms in $\bO_t \subset \bA_t$. For example in website recommender systems, if the user checks from the first recommended website and stops when she finds one interesting or has checked all websites, then the observed base arms are checked websites.

We use random variable $\bw_{t}(a) \in [0,1]$ as the {\em weight} of base arm $a$ at time $t$. Let $\cH_t$ denote the history before the learning agent chooses action at time $t$. Thus $\cH_t$ contains all information and observations at time $s < t$ and context information at time $t$. Given history $\cH_t$, we assume $\bw_{t,a}$'s are mutually independent and satisfy
\begin{equation} % eq:expectation
	% \label{eq:expectation}
	\EE[\bw_{t,a} | \cH_t] = \theta_{\ast}^{\top} x_{t,a},
\end{equation}
where $\theta_{\ast}$ is an unknown $d$-dimensional vector with the assumption that $\norm{\theta_{\ast}}_2 \leq 1$ and $0 \leq \theta_{\ast}^{\top} x_{t,a} \leq 1$ for all $t, a$.

We don't require the agent knows how the function $f(A, w)$ is defined. We only assume the agent has access to an oracle $O(A, w)$.

% We define random variable $\bO_t$ as the number of observed base arms in $\bA_t$, that is, for some $k=1,2,\ldots, \abs{\bA_t}$, 
% $$
% \bO_t = k, \text{ if } \bw_t(\ba_j^t)=0, \forall\, j < k \text{ and } \bw_t(\ba_k^t) = 1,
% $$
% or 
% $$
% \bO_t = \abs{\bA_t}, \text{ if }\bw_t(\ba_j^t) = 0, ~~ \forall\, j \leq \abs{\bA_t}.
% $$
% At the end of every time $t$, the agent observes the first $\bO_t$ items of $\bA_t$. We say that item $a$ is {\it observed} if $a = \ba_k^t$ for some $k \leq \bO_t$. 
% Thus, $\cH_t$ consists of $\{x_s, \bA_s = (\ba_{1}^s,...,\ba_{\abs{\bA_s}}^s), \bO_s, \bw_s(\ba_k^s),x_t \mid  k \in[\bO_s], 1 \le s<t \}$.

@@

@@

At time $t$, we denote $\EE_t[\cdot] = \EE[\cdot | \cH_t]$, where $\cH_t$ is the history a time $t$ before the learning agent chooses her action. By Equation \eqref{eq:expectation}, we have 
$$
  \EE[(\gamma_k \bw_{s,\ba_k^s}) | \cH_{s}] = \theta_*^{\top} (\gamma_k x_{s,\ba_k^s}).
$$
Using the ridge regression of data 
$$
  \{(\gamma_k x_{s,\ba_k^s}, \gamma_k \bw_{s,\ba_k^s})\}_{k \in[\bO_s], s\in[t]},
$$
we get an $l^2$-regularized least-squares estimate of $\theta_*$ with regularization parameter $\lambda > 0$:
\begin{equation}
  \hat{\theta}_t = (\bX_t^{\top}\bX_t + \lambda I)^{-1} \bX_t^{\top} \bY_t,
\end{equation}
where $\bX_t \in \RR^{(\sum_{s=1}^{t}\bO_s) \times d}$ is the matrix whose rows are $\gamma_k x_{s,\ba_k^s}^{\top}$ and $\bY_t$ is the column vector whose elements are $\gamma_k \bw_s(\ba_k^s)$, $k \in[\bO_s], s\in[t]$. Let
$$
  \bV_t = \bX_t^{\top} \bX_t + \lambda I = \lambda I + \sum_{s=1}^{t} \sum_{k=1}^{\bO_s} \gamma_k^2 x_{s,\ba_k^s}x_{s,\ba_k^s}^{\top}.
$$
Then $\bV_t \in \RR^{d \times d}$ is a symmetric positive definite matrix. 
For any symmetric positive definite matrix $V \in \RR^{d \times d} $ and any vector $x \in \RR^{d \times 1}$, we define the $2$-norm of $x$ based on $V$ to be $\norm{x}_V = (x^{\top} V x)^{\frac{1}{2}}$.
In the following, we will mainly use notations for the disjunctive objective when the two cases are similar.

@@

\begin{theorem}[\cite{abbasi2011improved}] %estimate of theta
  \label{thm:theta_estimate}
  Let 
  \begin{equation}
    \bbeta_{t}(\delta) = \sqrt{\ln\left(\frac{\det(\bV_{t})}{\lambda^d \delta^2}\right)} + \sqrt{\lambda}. \label{eq:definebeta}
  \end{equation}
  Then for any $\delta > 0$, with probability at least $1 - \delta$, for all $t > 0$, we have
  \begin{equation}
    \label{eq:estimateTheta}
    \norm{\hat{\theta}_t - \theta_{\ast}}_{\bV_{t}} \leq \bbeta_{t}(\delta).
  \end{equation}
\end{theorem}

@@

The fact that $\bU_t(a)$ is an upper confidence bound of expected weight $\theta_*^{\top}x_{t,a}$ is proved in the following lemma.
\begin{lemma} %estimate of U
  \label{lem:estimateU}
  When Eq.\eqref{eq:estimateTheta} holds for time $t-1$, we have
  $$
    0 \leq \bU_t(a) - \theta_{\ast}^{\top}x_{t,a} \leq 2\bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
  $$
\end{lemma}
\begin{proof}
  \begin{align*}
    \abs{\hat{\theta}_{t-1}^{\top}x_{t,a} - \theta_{\ast}^{\top}x_{t,a}} &\leq \norm{\hat{\theta}_{t-1} - \theta_{\ast}}_{\bV_{t-1}} \norm{x_{t,a}}_{\bV_{t-1}^{-1}} \\
    &\leq \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
  \end{align*}
\end{proof}

Our proposed algorithm, C$^3$-UCB, is described in Algorithm \ref{alg:ConComCascade}. 
First, the learning agent computes the upper confidence bounds (UCBs) $\bU_t \in [0,1]^{E}$ on the expected weights of all base arms in $E$. 
Second, she uses the computed UCBs $\bU_t$ to select an action $\bA_t$. 
Third, she plays $\bA_t$ and observes all feedback of base arms until first $0$ weight come out; the learning agent observes $\bO_t$ base arms and $\bw_t(\ba_k^t), k \in [\bO_t]$, where 
$$
  \bw_t(\ba_{k}^t) = \begin{cases} 0, ~~k < \bO_t\\ 1, ~~k = \bO_t\end{cases}
$$ 
or
$$
  \bw_t(\ba_k^t) = 0, k \leq \bO_t = \abs{\bA_t}.
$$
Then, the learning agent updates $\bV_t, \bX_t, \bY_t$ in order to get a newer estimate $\hat{\theta}_t$ of $\theta_*$ and new confidence radius $\bbeta_t(\delta)$. 
In this part, we use the notation $[A; B]$ to denote the matrix obtained by stacking A and B vertically like $\begin{pmatrix} A\\ B\end{pmatrix}$.

\begin{algorithm} %C^3-UCB algorithm
  \caption{C$^3$-UCB}
  \label{alg:ConComCascade}
  \begin{algorithmic}[1]
    \STATE {//Initialization}
    \STATE {Parameters: $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0$}
    \STATE {Parameters: $\delta > 0, \lambda \geq C_\gamma = \sum_{k=1}^{K} \gamma_k^2$}
    \STATE {$\hat{\theta}_0 = 0, \bbeta_0(\delta) = 1, \bV_0 = \lambda I, \bX_0=\emptyset, \bY_0=\emptyset$}

    \FORALL {$t=1,2,\ldots$}
      \STATE {Obtain context $x_{t,a}$ for all $a\in E$}
      \STATE {//Compute UCBs}
      \STATE {$\forall a\in E: $}
      \STATE {$\bU_t(a) \leftarrow \min\{\hat{\theta}_{t-1}^{\top}x_{t,a} + \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}, 1\}$}

>>>>

% my settings
\usepackage{amssymb,amsfonts,amsmath,bbm}
\usepackage{mathrsfs}
\usepackage[all]{xy}
\usepackage{empheq}
\usepackage{algorithm,algorithmic}
\usepackage{multirow}
\usepackage{ifthen}
\usepackage[usenames]{color}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{epstopdf}
%\usepackage{epsfig}
%\usepackage{times}
%\usepackage{helvet}
%\usepackage{courier}
%\usepackage{graphicx,subfigure}
%\usepackage{pdfpages}
%\usepackage{multirow}
%\usepackage{multicol}
\newcommand{\bbeta}{\boldsymbol{\beta}}
\newcommand{\EE}{\mathbb{E}}
\newcommand{\II}{\mathbb{I}}
\newcommand{\PP}{\mathbb{P}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\bT}{\mathbb{T}}
\newcommand{\bOne}{\mathbbm{1}}
\newcommand{\bA}{\mathbf{A}}
\newcommand{\ba}{\mathbf{a}}
\newcommand{\bB}{\mathbf{B}}
\newcommand{\bO}{\mathbf{O}}
\newcommand{\br}{\mathbf{r}}
\newcommand{\bU}{\mathbf{U}}
\newcommand{\bV}{\mathbf{V}}
\newcommand{\bw}{\mathbf{w}}
\newcommand{\bX}{\mathbf{X}}
\newcommand{\bY}{\mathbf{Y}}
\newcommand{\cA}{\mathcal{A}}
\newcommand{\cB}{\mathcal{B}}
\newcommand{\cH}{\mathcal{H}}
\newcommand{\cO}{\mathcal{O}}
\newcommand{\cS}{\mathcal{S}}
\newcommand{\argmax}{\mathrm{argmax}}
\newcommand{\trace}{\mathrm{trace}}
\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\norm}[1]{\| #1 \|}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{remark}[theorem]{Remark}
\newtheorem{proposition}[theorem]{Proposition}%[chapter]
\newtheorem{definition}[theorem]{Definition}%[chapter]
\newtheorem{corollary}[theorem]{Corollary}%[chapter]
\newtheorem{lemma}[theorem]{Lemma}%[chapter]
\newtheorem{example}[theorem]{Example}
\newenvironment{proof}{\noindent {\textbf{Proof. }}}{$\Box$ \medskip}

@@

% and / or case	
% \section{Problem Formulation}

% We formulate the problem of {\em contextual combinatorial cascading bandit} as follows. 
% Suppose we have a finite set  $E=\{1,...,L\}$ of $L$ \textit{ground items},  also referred to as {\em base arms}. 
% Let $\Pi^k=\{(a_1,...,a_k): a_1,...,a_k \in E, a_i \neq a_j \text{ for any } i \neq j\}$ be the set of all $k$-tuples of distinct items from $E$. 
% We call each of such tuples an {\em action} of length $k$. We will use $|A|$ to denote the length of an action $A$.
% Let $\Pi^{\leq K}= \cup_{k=1}^K \Pi^{k}$ denote the set of all actions with length at most $K$, and let $\cS \subseteq \Pi^{\leq K}$ be the set of \textit{feasible actions} with length at most $K$.

% As a convention, we always use boldface symbols to represent random variables.

% At time $t$, feature vectors $x_{t,a} \in \RR^{d \times 1}$ with $\norm{x_{t,a}}_2 \leq 1$ for every base arm $a \in E$ are revealed to the learning agent; the feature vectors combine both the information of the user and the corresponding base arm. \shengyu{Add a standard/typical example (just one sentence) to illustrate the combination?} Then the learning agent recommends a feasible action $\bA_t=(\ba_{1}^t,...,\ba_{\abs{\bA_t}}^t) \in \cS$ to a user, where notice that the length of the action is not fixed. Starting from the first item $\ba_{1}^t$, the user checks the items $(\ba_{1}^t,...,\ba_{\abs{\bA_t}}^t)$ one by one in that order. The checking process stops if the user clicks \shengyu{selects?} on one item or has checked all items without clicking \shengyu{selecting?} anyone. We use Bernoulli random variable $\bw_{t}(a) \in \{0,1\}$ as the {\em weight} of base arm $a$ at time $t$ to indicate whether the user has clicked on $a$ or not.

% Let $\cH_t$ denote the history before the learning agent chooses action at time $t$.
% Thus $\cH_t$ contains all information and observations at time $s < t$ and context information at time $t$. Given history $\cH_t$, we assume $\bw_{t,a}$'s are mutually independent and satisfy
% \begin{equation} % eq:expectation
%   \label{eq:expectation}
%   \EE[\bw_{t,a} | \cH_t] = \theta_{\ast}^{\top} x_{t,a},
% \end{equation}
% where $\theta_{\ast}$ is an unknown $d$-dimensional vector with the assumption that $\norm{\theta_{\ast}}_2 \leq 1$ and $0 \leq \theta_{\ast}^{\top} x_{t,a} \leq 1$ for all $t, a$. 
% We define random variable $\bO_t$ as the number of observed base arms in $\bA_t$, that is, for some $k=1,2,\ldots, \abs{\bA_t}$, 
% $$
%   \bO_t = k, \text{ if } \bw_t(\ba_j^t)=0, \forall\, j < k \text{ and } \bw_t(\ba_k^t) = 1,
% $$
% or 
% $$
%   \bO_t = \abs{\bA_t}, \text{ if }\bw_t(\ba_j^t) = 0, ~~ \forall\, j \leq \abs{\bA_t}.
% $$
% At the end of every time $t$, the agent observes the first $\bO_t$ items of $\bA_t$. We say that item $a$ is {\it observed} if $a = \ba_k^t$ for some $k \leq \bO_t$. 
% Thus, $\cH_t$ consists of $\{x_s, \bA_s = (\ba_{1}^s,...,\ba_{\abs{\bA_s}}^s), \bO_s, \bw_s(\ba_k^s),x_t \mid  k \in[\bO_s], 1 \le s<t \}$.

@@

At time $t$, feature vectors $x_{t,a} \in \RR^{d \times 1}$ with $\norm{x_{t,a}}_2 \leq 1$ for every base arm $a \in E$ are revealed to the learning agent; the feature vectors combine both the information of the user and the corresponding base arm. \shengyu{Add a standard/typical example (just one sentence) to illustrate the combination?} For example, suppose the user at time $t$ is represented by the feature vector $u_t$ and the feature vector of the base arm $a$ is $v_a$, then we can let $x_{t,a}$ be $(u_t, v_a)$ which combines both the information of the user and the base arm. \shuai{I have added one sentence.} Then the learning agent recommends a feasible action $\bA_t=\{ \ba_{1}^t,...,\ba_{\abs{\bA_t}}^t \} \in \cS$ to the user and notice that the size of the action is not fixed. Then according to the user behavior and the structure of the action $\bA_t$, we observe the weights of fist $\bO_t$ base arms in $\bA_t$. For example in website recommender systems, if the user checks from the first recommended website and stops when she finds one interesting or has checked all websites, then the observed base arms are checked websites.

Let $\cH_t$ denote the history before the learning agent chooses action at time $t$. Thus $\cH_t$ contains all information and observations at time $s < t$ and context information at time $t$. Given history $\cH_t$, we assume $\bw_{t,a}$'s are mutually independent and satisfy
\begin{equation} % eq:expectation
  \label{eq:expectation}
  \EE[\bw_{t,a} | \cH_t] = \theta_{\ast}^{\top} x_{t,a},
\end{equation}
where $\theta_{\ast}$ is an unknown $d$-dimensional vector with the assumption that $\norm{\theta_{\ast}}_2 \leq 1$ and $0 \leq \theta_{\ast}^{\top} x_{t,a} \leq 1$ for all $t, a$.

We define random variable $\bO_t$ as the number of observed base arms in $\bA_t$. At the end of every time $t$, the agent observes the first $\bO_t$ items of $\bA_t$. We say that item $a$ is {\it observed} if $a = \ba_k^t$ for some $k \leq \bO_t$. Thus, $\cH_t$ consists of $\{x_s, \bA_s = (\ba_{1}^s,...,\ba_{\abs{\bA_s}}^s), \bO_s, \bw_s(\ba_k^s),x_t \mid  k \in[\bO_s], 1 \le s<t \}$.

We consider the position discount. For example in recommender systems, the positions to display advertisements might have difference prices, hence of different value when user clicks on it.

We don't require the agent knows how the function $f(A, w)$ is defined. We only assume the agent has access to an oracle $\cO(A, w)$. More precisely, an oracle $\cO(\cS, w)$ is  called an $\alpha$-approximation oracle for some $\alpha \leq 1$, if given input $w$ and $\cS$, the oracle always returns an action(super arm) $A = \cO(r, \cS) \in \cS$ satisfying $f(w, S) \geq \alpha opt_{w, \cS}$ where $opt_{w, \cS} = \max_{s \in \cS}$ f(r, S).

The $\alpha$-regret on time $t$ can be written as
$$
R_t = \alpha opt_{w_t} - f(w_t, A_t).
$$
Our goal is to minimize the cumulative regret $R = \sum_{t=1}^n R_t$.

@@

At time $t$, we denote $\EE_t[\cdot] = \EE[\cdot | \cH_t]$, where $\cH_t$ is the history a time $t$ before the learning agent chooses her action. By Equation \eqref{eq:expectation}, we have 
$$
  \EE[(\gamma_k \bw_{s,\ba_k^s}) | \cH_{s}] = \theta_*^{\top} (\gamma_k x_{s,\ba_k^s}).
$$
Using the ridge regression of data 
$$
  \{(\gamma_k x_{s,\ba_k^s}, \gamma_k \bw_{s,\ba_k^s})\}_{k \in[\bO_s], s\in[t]},
$$
we get an $l^2$-regularized least-squares estimate of $\theta_*$ with regularization parameter $\lambda > 0$:
\begin{equation}
  \hat{\theta}_t = (\bX_t^{\top}\bX_t + \lambda I)^{-1} \bX_t^{\top} \bY_t,
\end{equation}
where $\bX_t \in \RR^{(\sum_{s=1}^{t}\bO_s) \times d}$ is the matrix whose rows are $\gamma_k x_{s,\ba_k^s}^{\top}$ and $\bY_t$ is the column vector whose elements are $\gamma_k \bw_s(\ba_k^s)$, $k \in[\bO_s], s\in[t]$. Let
$$
  \bV_t = \bX_t^{\top} \bX_t + \lambda I = \lambda I + \sum_{s=1}^{t} \sum_{k=1}^{\bO_s} \gamma_k^2 x_{s,\ba_k^s}x_{s,\ba_k^s}^{\top}.
$$
Then $\bV_t \in \RR^{d \times d}$ is a symmetric positive definite matrix. For any symmetric positive definite matrix $V \in \RR^{d \times d} $ and any vector $x \in \RR^{d \times 1}$, we define the $2$-norm of $x$ based on $V$ to be $\norm{x}_V = (x^{\top} V x)^{\frac{1}{2}}$.
%In the following, we will mainly use notations for the disjunctive objective when the two cases are similar.

@@

\begin{lemma} $\mathrm{\cite{abbasi2011improved}}$ %estimate of theta
  \label{thm:theta_estimate}
  Let 
  \begin{equation}
    \bbeta_{t}(\delta) = \sqrt{\ln\left(\frac{\det(\bV_{t})}{\lambda^d \delta^2}\right)} + \sqrt{\lambda}. \label{eq:definebeta}
  \end{equation}
  Then for any $\delta > 0$, with probability at least $1 - \delta$, for all $t > 0$, we have
  \begin{equation}
    \label{eq:estimateTheta}
    \norm{\hat{\theta}_t - \theta_{\ast}}_{\bV_{t}} \leq \bbeta_{t}(\delta).
  \end{equation}
\end{lemma}

@@

The fact that $\bU_t(a)$ is an upper confidence bound of expected weight $w_{t, a} = \theta_*^{\top} x_{t,a}$ is proved in the following lemma.
\begin{lemma} %estimate of U
  \label{lem:estimateU}
  When Eq.\eqref{eq:estimateTheta} holds for time $t-1$, we have
  $$
    0 \leq \bU_t(a) - w_{t,a} \leq 2 \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
  $$
\end{lemma}
\begin{proof}
	$w_{t, a} = \theta_*^{\top} x_{t,a}$. First by Holder's inequality,
	\begin{align*}
		\abs{\hat{\theta}_{t-1}^{\top}x_{t,a} - \theta_{\ast}^{\top}x_{t,a}} &\leq \norm{\hat{\theta}_{t-1} - \theta_{\ast}}_{\bV_{t-1}} \norm{x_{t,a}}_{\bV_{t-1}^{-1}} \\
		&\leq \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
	\end{align*}
	Then
	\begin{align*}
		\bU_t(a) - w_{t,a} &\leq \hat{\theta}_{t-1}^{\top}x_{t,a} + \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}} - \theta_{\ast}^{\top}x_{t,a} \\
		&\leq 2 \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}},
	\end{align*}
	and 
	\begin{align*}
		&\bU_t(a) - w_{t,a} \\
		&\qquad \geq \min\{\hat{\theta}_{t-1}^{\top}x_{t,a} + \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}} - \theta_*^{\top} x_{t,a}, 1 - \theta_*^{\top} x_{t,a}  \} \\
		&\qquad \geq 0		
	\end{align*}
\end{proof}

Our proposed algorithm, C$^3$-UCB, is described in Algorithm \ref{alg:ConComCascade}. First, the learning agent computes the upper confidence bounds (UCBs) $\bU_t \in [0,1]^{E}$ on the expected weights of all base arms in $E$. Second, she uses the computed UCBs $\bU_t$ to select an action $\bA_t$. Third, she checks from the first base arm in $\bA_t$ and stops after checking the $\bO_t$-th base arm.
% Third, she plays $\bA_t$ and observes all feedback of base arms until first $0$ weight come out; the learning agent observes $\bO_t$ base arms and $\bw_t(\ba_k^t), k \in [\bO_t]$, where 
% $$
%   \bw_t(\ba_{k}^t) = \begin{cases} 0, ~~k < \bO_t\\ 1, ~~k = \bO_t\end{cases}
% $$ 
% or
% $$
%   \bw_t(\ba_k^t) = 0, k \leq \bO_t = \abs{\bA_t}.
% $$
Then, the learning agent updates $\bV_t, \bX_t, \bY_t$ in order to get a newer estimate $\hat{\theta}_t$ of $\theta_*$ and new confidence radius $\bbeta_t(\delta)$. 
In this part, we use the notation $[A; B]$ to denote the matrix obtained by stacking A and B vertically like $\begin{pmatrix} A\\ B\end{pmatrix}$.
